---
title: "FPN Exit Survey"
output: html_document
---

```{r setup}
library(readr)
library(tidyverse)
```
This is the beginning to my report. Here's the survey data from Firefox Private Network.


```{r include=FALSE}
setwd('~/codespace/intro_to_rstudio_tidyverse')
data <- read_csv("data/private network - exit survey - 20191114142053-SurveyExport.csv")
glimpse(data)
```
Let's look at the responses from the question, `Why did you uninstall the Firefox Private Network?`.

```{r message=FALSE, warning=FALSE}
ggplot(data=data) + geom_histogram(mapping=aes(x=`Why did you uninstall the Firefox Private Network?`), stat="count")
```
It seems that the most common response for this question was that "It was not working correctly". That's a bummer :/

Hmm...also, the axes on the plot isn't particularly easy to read. Let's see if we can correct this.

```{r message=FALSE, warning=FALSE}
# Found out how to wrap text on stackoverflow: https://stackoverflow.com/questions/21878974/auto-wrapping-of-labels-via-labeller-label-wrap-in-ggplot2
library(stringr)

ggplot(data=data) + 
  geom_histogram(mapping=aes(x=`Why did you uninstall the Firefox Private Network?`), stat="count") +
  # this is special sauce
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))
```

Let's check out another question.
```{r message=FALSE, warning=FALSE}
ggplot(data=data) + 
  geom_histogram(mapping=aes(x=`What sort of problems did you have with Firefox Private Network?`), stat='count') + 
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))
```
```{r message=FALSE, warning=FALSE}
ggplot(data=data) + 
  geom_histogram(mapping=aes(x=`What sort of problems did you have with Firefox Private Network?`, color=`Why did you uninstall the Firefox Private Network?`), stat='count') + 
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  theme(legend.position="bottom")
```


